Staged Abstract Interpreters

### 2018-10-18 paper/10_intro.tex
intro

>>>>

1. we know how to stage an interpreter, natural to ask how to stage an abstract interpreter, given 
the structural similarity of interpreters and abstract interpreters.

2. whole-program analysis is slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

3. analyzing modern programs with large libraries are expensive, we need to a way to create
summaries of libraries so that we can reuse them.
